### 2020-03-14 myPapers/NFES_Review/SUPPLEMENTARY_INFORMATION_Polymers_for_Nearfield_Electrospinning_with_Spatial_Control/article.tex
organising my directories ...

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
\documentclass[5p,,preprint,12pt,twocolumn]{elsarticle}
\makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Feature enabled:
%toc: yes
%bookmark: yes
%pagenum: yes
%text-layout: twocolumn
%endfloat: placeins
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\@ifpackageloaded{hyperref}{\def\alreadybookmark{}}{\usepackage[hidelinks]{hyperref}}
\@ifpackageloaded{bookmark}{}{\usepackage{bookmark}}
\makeatother
\ifdefined\alreadybookmark\def\pdfbookmark[#1]#2#3{}\fi
\makeatletter
\def\ps@pprintTitle{\save@ps@pprintTitle\gdef\@oddfoot{\footnotesize\hspace*{.5\textwidth}\thepage\itshape \null\hfill\today}}
\makeatother
          \makeatletter\@ifundefined{tableofcontents}{\usepackage{typeset-custom-toc}}{}\makeatother
\usepackage[section]{placeins}

\usepackage{etoolbox}

@@

\usepackage{float}

@@

\begin{document}
\pdfbookmark[title]{Polymers for Near-field Electrospinning with Spatial Control}{title}

@@

\title{Polymers for Near-field Electrospinning with Spatial Control
}

@@

\begin{abstract}
Near-field electrospinning (NFES) is identified to be a technique able to fabricate polymer nano and micro fibers with accurate placement. In the past years (2006-2019), several polymer solutions have been successfully electrospun into fibers through several variants of the conventional NFES process. Each NFES variant intents to tailor the process parameters in order to improve the fibers' properties. This paper presents a review on the research and related development of electrospun fibers, emphasizing the used polymers, solvents, and fiber characteristics. Relevant summary of polymer solutions and near-field electrospinning processing conditions is provided in this paper.
\end{abstract}
\begin{keyword} 
polymer\sep solvent\sep near-field electrospinning\sep NFES\sep fibers\sep spatial control
\end{keyword}

\end{frontmatter}
\tableofcontents

\section{Fabrication Processes of Polymer Fibers}
~Even though electrospinning is an old invention \unskip~\cite{527120:12073288}, it is currently a trending topic among researchers \unskip~\cite{527120:12073453,527120:12073495,527120:12073496}. One of the reasons electrospinning is to be studied is its potential to fabricate polymer nano fibers from a variety of polymers. The technique allows the production of thin continuous fibers with ease, with diameters down to 3 $nm $ in some cases, which is something difficult to achieve by other techniques. Furthermore, the basic setup can be modified with ease to fabricate different fibers with diversified functionalities with different materials. The produced fibers can be aligned or unaligned. Besides, the electrospinning equipment is inexpensive and of small size, compared to the equipment of standard spinning techniques\unskip~\cite{527120:12073538}. On the other hand, the understanding of the electrospinning process has improved in the last years.

Current literature dictates the typical spinning setup is comprised by three main components: a syringe needle, a fiber collector, and some way to dispense the fibers from the needle to the collector. The spinning process is an electrohydro-dynamic (EHD) technique that yields continuous polymer fibers. Other EHD techniques are spraying and atomization which produce polymer droplets and polymer particles respectively.

\bgroup
\fixFloatSize{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}{\includegraphics{images/f10bcbc9-719b-4a8d-8a38-930cc6ea2d0f-uimg_ehdprocesses.jpg}}{}
\makeatother 
\caption{{Electrohydro-dynamic techniques}}
\label{f-02e0e3cf88d6}
\end{figure}
\egroup

\subsection{Polymer reservoir: Polymer melt \& Polymer solution}Another electrospinning classification is the melt process. As Brown et al. \unskip~\cite{527120:13445499} discussed, the polymer melt is equivalent to the polymer solution electrospinning (in place of a polymer solution a melt is used). The use of a polymer melt increases the complexity of the process, because the nozzle syringe and spinneret required to be heated to maintain the polymer in a liquid state. The fibers produced in melt spinning are typically found to have larger diameters than those from the polymer solutions due to the higher viscosity of a polymer melt than its solution. The apparatus used by Brown et al. \unskip~\cite{527120:13445499} is depicted in .

[TODO: draw an apparatus used for melt electrospinning].

Despite the added complexity and thicker diameters, melt electrospinning  gets around the need to handle volatile solvents, making the process safer to be performed on larger scales, On the other hand, this technique gets rid of any solvent contamination.

The first report of a melt electrospun drug delivery system came from Nagy et al. \unskip~\cite{527120:13445555}, who prepared fibers by melt electrospinning of Eudragit EPO with carvedilol. The drug and polymer were melted and mixed to form a homogeneous solid mixture prior to spinning. The melt-spun fibers reached diameters of 5{\textendash}30 $\mu m $, compared to 300{\textendash}1000 $nm $ diameters produced from solution-spun fibers.

This work has been built on to blend plasticisers with the polymer Eudragit EPO and carvedilol active ingredient.\unskip~\cite{527120:13445752} The plasticisers Triacetin, Tween 80 and Polyethylene Glycol were investigated by Attila et al. in order to reduce the melting point of the polymer-drug mixture. The temperature drop is desirable to minimize the occurring drug degradation.

Lian and Meng\unskip~\cite{527120:13445754} performed a comparison of poly(\ensuremath{\varepsilon }-caprolactone) (PCL) fibers fabricated by the melt and solution electrospinning techniques. Lian and Meng\unskip~\cite{527120:13445754} reported that melt spinning is preferable when the polymer presents a low solubility, on the other hand the melt fibers were produced in a slower release rate.  Lian and Men findings feature the solution-spun fibers to have a porous structure. Gernot et al.\unskip~\cite{527120:13534159} demonstrated that submicron-size fibers are possible through melt electrospinning. In their effort, they achieved a precise deposition of PCL fibers with diameters of $817 \pm 165 nm $.

In literature, melt electrospinning has less evidence than the solution approach. However, melt electrospinning arises to be as flexible as its solution counterpart in handling multiple polymers, as reported in McCann's work\unskip~\cite{527120:13534572}. Currently, the melt electrospinning setup is harder to establish but the lack of research on this technique explains its unexplored potential.

\subsection{Dispensing nozzle}Coaxial electrospinning (co-electrospinning) requires de implementation of a dual needle nozzle, where one needle is nested concentrically inside another needle [TODO: draw nested needles]. \unskip~\cite{527120:13914792,527120:13914793} The purpose of the co-electrospinning setup is to produce core/shell fibers, unlike mono axial electrospinning that yields monolithic fibers. Sun et al. \unskip~\cite{527120:13914312} addressed electrospinning setups, where both the core and shell are comprised by PEO (poly(ethylene oxide)) and for a PEO shell with a poly(dode-cylthiophene) core. Sun et al. state that co-electrospinning has the potential to extend the range of materials that can be used for electrospinning. The shell solution can be modified to make the core solution spunable. It was also discovered that non-spunable solutions can by implemented as shell solutions in conjunction with a spunable core solution. \unskip~\cite{527120:13914968}

Some advantages that co-electrospinning setups can offer include the preempting the initial jet burst from the spinneret nozzle. On the other hand, as the morphology and shape of the fibers depend on the polymer solution properties, the use of a co-axial nozzle allows the amendment of the material properties by producing bubbles, scaffolds and particles. \unskip~\cite{527120:13914748,527120:13914750}. As in conventional NFES, in co-electrospinning, the needle tip is connected to a high voltage power supply with a grounded collector. With the influence of high electric fields, the fibers are prone to brake into separate layers due to the whipping instabilities as the jet travels to the substrate. The instability can be mitigated by adding additional ring electrodes between the spinneret and the grounded collector. \unskip~\cite{527120:13915304}

\subsection{Stretching forces}

\subsubsection{Electric Field}Electrospinning (electrostatic fiber spinning) is a fiber fabrication approach that implements an electric field produce fibers by an electrical potential difference between the syringe needle and the collector. The typical electrospinning setup applies an electrostatic charge to the polymer fluid at the tip of the needle nozzle, which results in the formation of the Taylor cone \unskip~\cite{527120:13659828}, from which a single polymer jet is ejected to the grounded collector. From the Taylor cone, the supplied polymer jet (typically a polymer solution) accelerates and reduces in diameter. The fiber finally develops with the complete solvent evaporation. Electrospun fibers are prone to splitting with the increase in acceleration, where multiple fibers are yield in a process known as electrospraying \unskip~\cite{527120:13659925}.

The electrospinning process starts with charging a polymer solution droplet. When a polymer solution is administrated with a syringe pump, solution droplets will fall under the influence of gravity. The solution dripping stops when the electric field is strong enough to break the solution's surface tension, causing the droplet to change shape forming a polymer solution jet\unskip~\cite{527120:12033655}.

Shin et al. \unskip~\cite{527120:13659926} reported that the growth of the whipping instability is one important element within the electrospinning technique. As detailed in Shin's work, weak electric fields produce a single uniformly thinning jet, and strong electric fields the jet becomes unstable after traveling a short distance.

\paragraph{High voltage power supply: Direct Current \& Alternating Current}Direct current (DC) is typically used in electrospinning with the electrons flowing in one direction. Alternate current (AC) implementations are also studied as the AC creates a change in the direction of the current flow. Kessick et al.\unskip~\cite{527120:13444381} demonstrated the implementation of AC power supplies in the production of polymer fibers.

The AC electrospinning setup is similar to that for the DC variant. AC electrospinning apparatus do not require a grounded collector as the current alternates. In AC, the produced fibers are prone to carry an electric charge, while those generated shortly after have an opposite charge. The difference in charges lead the fibers to discharge on each other, creating an aerogel plume of fibers. The optimal AC frequency depends on the materials used and is typically within of 50 $Hz $ {\textendash} 1 $kHz $. \unskip~\cite{527120:13443405}

The AC technique has been studied for drug loaded related applications. Balogh et al. \unskip~\cite{527120:13445177} compared fibers fabricated by DC and AC spinning techniques. They produced fibers by using three polymers: Eudragit EPO (cationic copolymer), Eudragit L100-55 (anionic polymer) and poly(vinyl pyrrolidone) (PVP) (neutral polymer). Balogh et al. discovered AC and DC electrospinning can produce fibers with all three polymers. However, The AC process allowed the implementation of faster flow rates than in the DC setup. The DC electrospinning technique generated fibers with a maximum flow rate of 5 $ml/h $; on the other hand, the AC setup allowed an increase in flow rate up to 40 $ml/h $. AC electrospinning approach is as effective as the DC technique in producing drug delivery systems.

\subsubsection{Centrifugal force}The spinning processes require the implementation of a force to break the polymer source into a polymer jet. Centrifugal spinning intends to produce fibers by the use of a rotating polymer source. The centrifugal force generated from typical rotatory speeds above 2000 rpm, results in fiber formation. \unskip~\cite{527120:13535559,527120:13535561}.

The centrifugal force technique is applied to polymer solutions and melts. This approach is used in applications were the precise deposition of the fibers is not relevant and production rate is to be maximized \unskip~\cite{527120:13535894}.  Efforts in centrifugal spinning are focused on drug delivery applications. Zander \unskip~\cite{527120:13535977} fabricated polycaprolactone (PCL) fibers using the solution and melt variants of the centrifugal approach. Zander's fibers were produced with rotatory speed between three and 18 thousand revolutions per minute with $10 \mu m $ in diameter.

On the other hand, PCL and PVP fibers were generated by Amalorpava et al. \unskip~\cite{527120:13536089}.  Amalorpava achieved sub micron/size fiber diameters for drug release purposes and bacteria growth inhibition properties. Literature\unskip~\cite{527120:13536446} has shown that centrifugal approach has a simple setup that promises a large scale fabrication of fibers.

In some cases the centrifugal force implementations and pressurized gyration can be combined with an electric field. The implementation of two stretching forces (centrifugal and electrical forces), can help solvent evaporation\unskip~\cite{527120:13536560}. Centrifugal electrospinning implements the same setup as the standard centrifugal spinning with the addition of a high voltage power supply between the rotating dispensing nozzle and the collector. The combined method has evidence to yield parallel fibers\unskip~\cite{527120:13536841,527120:13536900,527120:13537392,527120:13537393} at a higher rate \unskip~\cite{527120:13536841,527120:13536900} than the standard electrospinning approach.

\subsubsection{Blowing forces}Nano fibers can be produced with the implementation of pressurized gas with a polymer solution. The setup used for blow spinning is similar to the one used in standard electrospinning, where the polymer precursor is dispensed at a controlled rate. Unlike traditional electrospinning, in the solution blow spinning setup the needle nozzle applies pressurized gas to the polymer solution through an outer spinneret\unskip~\cite{527120:13538056}.

[TODO: draw an apparatus used for solution blow spinning or melt blowing] \unskip~\cite{527120:13538056}.

Poly(lactic acid) (PLA) fibers have been produced by solution blow spinning. Oliveira et al. \unskip~\cite{527120:13539278} fabricated the fibers from $6 wt\% $ PLA solutions with progesterone for live stock reproductive cycle regulation applications. On the other hand, Souza et al.\unskip~\cite{527120:13538056} conducted a study to compare the standard electrospinning and the solution blow spinning techniques. Poly(3-hydroxybutyrate-co-3-hydroxyvalerate) were fabricated by both methods. The fibers produced by electrospinning had thicker diameters and their size uniformity was higher in the fibers produced by solution blow spinning.

Jiang et al.\unskip~\cite{527120:13554126} combined the blowing technique with the electrospinning approach. The blow electrospinning technique implements both electric and gas flow forces to stretch the fibers. Jiang used an apparatus similar to those used in traditional electrospinning. The experimental setup requires a coaxial needle nozzle with a pressurized gas flow along with a potential difference between the dispensing needle and the grounded collector.

[TODO: draw Figure apparatus used for solution blow spinning or melt blowing]

\subsubsection{Mechanical force}Mechanical drawing comprises the simple technique to produce fibers by stretching the polymer solution with a glass pipette. \unskip~\cite{527120:14024998} Nevertheless, the drawing technique is not scalable or with practical applications. \unskip~\cite{527120:14025041} Touch-spinning methods have been developed to introduce a scalable technique for the production of nano fibers. Touch-spinning comprises a rotating stage with an embedded glass rod. [TODO: draw touch spinning setup]. Where a polymer solution is supplied from a syringe needle such that the tip of the glass rod makes contact with the polymer solution as it rotates, creating fibers. The rotation stretches the fiber, causing the fiber to increase in length and decrease in diameter. The increase in length causes the fiber surface are to increase and therefore making the polymer solution solvent to volatilize, ending with a dry fiber within the collector.

The touch spinning technique implies that the fiber diameter can be controlled by the rotation speed and the polymer solution concentration. The main difference relays on the fact that the touch spinning method implements mechanical control to manipulate and stretch the fibers during the fabrication process, guiding the fiber in the collector enabling better control over fiber alignment.\unskip~\cite{527120:14091959}

\subsubsection{Microfluidic forces}The microfluidic spinning technique manipulates and controls the polymer solution in networks of micrometer channels. The channel network are typically embedded in a microfluidic chip, where the solution deposition rate is controlled by active components (pumps and valves) with a computer. Cheng et al. \unskip~\cite{527120:13656236} compared and combined the microfluidic spinning and electrospinning techniques.

On the other hand, Kang et al. \unskip~\cite{527120:13656548} managed to fabricate micro fibers by imitating the "silk spinning" process of spiders. Kang's micro fibers properties were modified using a microfluidic system with a programmable flow control. The current microfluidic spinning approach is not scalable to a large fiber production, however it enables the fabrication of high-complex fibers that are not easily achieved by other methods.

[TODO: draw Figure apparatus used for microfluidic spinning]

Microfluidic techniques offer the possibility to embed several components into a single fiber, where each component can be released at different parts of the fiber.

\subsection{Nozzle-to-substrate distance}[TODO: draw FFES setup], depicts the typical setup for the conventional far-field electrospinning (FFES). As stated in previous sections, the precursor polymer droplet becomes charged with the employment of an electric field between the polymer solution and the collector\unskip~\cite{527120:14135125}. When the polymer solution surface tension is overcome by the electric field potential difference a jet is formed, starting the electrospinning process. The electrospinning process can be break down into two steps: i) first the jet travels in a straight line, and ii) the jet begins to curl due to bending and whipping instabilities \unskip~\cite{527120:13444381,527120:14135543}. The fiber spatial control in far-field electrospinning is limited due to the instabilities, inhibiting the precise deposition of fibers.

In the intent to achieve controlled fiber deposition, Sun et al. \unskip~\cite{527120:11974321} reported an electrospinning variation known as near-field electrospinning (NFES). [TODO: draw NFES setup], describes the near-field electrospinning setup, where the distance between the dispensing nozzle and the collector is reduced to write fibers while the jet travels in a straight line. Moreover, some mechanical influence is required to deposit fibers precisely. The mechanical force is introduced by moving collector. If the polymer solution jet speed is faster than the speed of the moving collector, the written fiber will curl; on the other hand, if the collector moves faster than the polymer jet, the fiber will gradually diminish \unskip~\cite{527120:11974327,527120:11974326}. Currently, due to the lack of theoretical models, the near-field electrospinning process parameters (such as the collector speed) are typically tuned by experience and experimentation only.

The main difference between NFES and FFES is the distance between the needle and the collector which is higher in FFES (about 10 cm) compared to NFES which ranges in the mm scale. The short distance allow the production of well aligned fibers within particular designs. [7]

\bgroup
\fixFloatSize{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}
\begin{figure}[!htbp]
\centering \makeatletter\IfFileExists{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}{\includegraphics{images/461590fc-21b9-4974-88ef-bdfb00006f73-udrf_nfes.jpg}}{}
\makeatother 
\caption{{Typical near-field electrospinning set-up \unskip~\protect\cite{527120:11973130}.}}
\label{f-8e5a75d9ba17}
\end{figure}
\egroup

\section{Properties that Improve Accuracy of Nano-Fiber Deposition}
Near-field electrospinning is considered to be an outstanding technique to fabricate polymer fibers with spatial control and it has suffered several modifications to improve the precision and accuracy of the fiber deposition. This paper intents to collect the NFES variants of electrospunable polymer solutions with spatial control in recent research.

\subsection{Low-Voltage NFES (LV NFES) \unskip~\protect\cite{527120:11973130}}Some differences have been discovered between LV-NFES and conventional NFES. Low voltage near field electrospinning produces thinner fibers with lower voltages. Moreover, when implementing a moving stage, the fibers are affected by the mechanical stretching. Bisht et al. \unskip~\cite{527120:11973130} reported that thinner diameters are yield with the increase of the x-y stage velocity, and larger diameters by decreasing the stage velocity.

-{\textgreater} A continuous method for controlled electrospinning of polymeric nano fibers on two-dimensional (2D) and three-dimensional (3D) substrates using low voltage near-field electrospinning (LV NFES). The method overcomes some of the drawbacks in more conventional near-field electrospinning by using a super elastic polymer ink formulation. The visco-elastic nature of our polymer ink enables continuous electrospinning at a very low voltage of 200 V, almost an order of magnitude lower than conventional NFES, thereby reducing bending instabilities and increasing control of the resulting polymer jet. In one application, polymeric nano fibers are freely suspended between micro structures of 3D carbon on Si substrates to illustrate wiring together 3D components in any desired pattern.{\textless}-

\subsection{Scanning Tip Electrospinning \unskip~\protect\cite{527120:11974306}}-{\textgreater} A continuous near-field electrospinning (NFES) process has been developed to deposit solid nano fibers with orderly patterns over large areas. Before the onset of electrospinning, a bias voltage is applied to a semi-spherical shaped polymer droplet outside of a syringe needle, and a probe tip mechanically draws a single fiber from the droplet to initiate continuous NFES. Contrary to the conventional electrospinning process, we show that decreasing electrical field in continuous NFES results in smaller line width deposition, and nano fibers can be assembled into controlled complex patterns such as circular shapes and grid arrays on large and flat areas. {\textless}-

\subsection{3D Electrospinning \unskip~\protect\cite{527120:11974313} \mbox{}\protect\newline Electrohydro-dynamic 3D Print-patterning or Electrohydro-dynamic Jetting \unskip~\protect\cite{527120:11974310}}-{\textgreater} Characterized the behavior of polymer jet from near-field electrospinning onto the ink-jet patterned paper with conductive Ag nano particles in order to form the controlled three-dimensional nano structures. Using ink-jet patterned paper with conductive ink as a collector, the polymer jet is induced to the pre patterned shape through the concentrated electric field caused by singularity between the spinneret and the printed patterns. Due to the electric field enhancement of the deposited electrospun fiber, an additionally spun fiber can be stacked on the deposited fibers directly. Therefore, the controlled three-dimensional nano/micro structures can be successfully realized by the proposed method. We characterized the deposition of the electrospun fiber according to the distance between the ink-jet printed pattern and the spinneret. In addition, the sharp edged three-dimensional micro-structures were fabricated by carrying out the electrospinning on the patterns with various angled edges. A CCD camera was used to observe the behavior of the polymer jet, and the SEM image was analyzed to confirm that the fibers are stacked as desired.

Uncover a new method for the preparation of bio-polymer scaffolds and demonstrate its potential for the development of organs with the aid of tissue engineering. Two novel nano-composite polymers, a non-biodegradable polyhedral oligomeric silsesquioxane-poly (carbonate-urea)urethane and a biodegradable polyhedral oligomeric silsesquioxane-polycaprolactone-poly(carbonate-urea)urethane, have been subjected to flow in an electric field. Electrically forced micro-threading of the polymers occurs and a three-dimensional print-patterning device was used to deposit fine (⬍50 \ensuremath{\mu}m) threads of polymer according to a pre-designed architecture to prepare scaffolds. The technique can offer tremendous potential in the development of organs. {\textless}-

\subsection{Multinozzle NFES \unskip~\protect\cite{527120:11974322,527120:11974323,527120:11974324}}-{\textgreater} Multinozzle electrospinning systems are designed to increase productivity, while near-field electrospinning (NFES) systems are designed to deposit solid nano fibers in a direct, continuous, and controllable manner. In this paper, several multinozzle NFES setups are tested. The experiment reveals that the deposition distance becomes larger when working distance and needle spacing increase, and the influence of voltage is relatively weaker. The deposition of double nozzle NFES has been studied with Coulomb's law and theoretical derivation has been verified by the experimental conclusion. The experiment result and theoretical derivation are helpful to get different distance of direct-written fibers by adjusting working distance or needle spacing to change distance of fibers largely and adjusting voltage to change distance slowly. Through these efforts, it is convenient to adjust the distance of straight fibers in multinozzle system. [1]

For large area micro/nano pattern printing, multi-nozzle electrohydrodynamic (EHD) printing setup is an efficient method to boost productivity in near-field electrospinning (NFES) process. And controlling EHD multi-jet accurate deposition under the interaction of nozzles and other parameters are crucial concerns during the process. The influence and sensitivity of various parameters such as the needle length, needle spacing, electrode-to-collector distance, voltage etc. on the direct-write patterning performance was investigated by orthogonal experiments with dual-nozzle NFES setup, and then the deposition distance estimated based on a novel model was com- pared with measurement results and proven. More controllable deposition distance and much denser of aligned nano fiber can be achieved by rotating the dual-nozzle setup. This study can be greatly contributed to estimate the deposition distance and helpful to guide the multi-nozzle NFES process to accurate direct-write pattern in manufacturing process in the future.

To mass-volume fabricate micro- and nano scales aligned pattern, multi-nozzle near- field electrospinning (NFES) direct-writing technology is well proposed as a high- efficiency method in electrohydrodynamic (EHD) printing process. However, the interference effect among adjacent nozzles and coupling effect of various parameters have restricted to investigate deposition characteristic of multi-nozzle NFES and control EHD multi-jet deposition accuracy. In order to improve the accuracy of EHD multi-jet deposition with high-efficiency printing process, the experimental result compared with theoretical method were discussed. In this work, the influence of multi-nozzle geometry distribution and electrospinning parameters on deposition characteristic was studied with multi-nozzle NFES setup, and nozzles were in linear array. The deposition distance and homogeneity of aligned nano fibers were measured and explained with coefficient of dispersion on electric field among nozzles by simulation. Moreover, deposition distance of multi-nozzle NFES process was evalu- ated by modified theoretical derivation based on our previous studies. The modified theoretical derivation showed a good agreement with experiment results, and indicated that multi-nozzle NFES could accurately and efficiently direct-write aligned array pattern in the future. {\textless}-

\subsection{Electrohydro-dynamic Writing or Mechanoelectrospinning (MES) \unskip~\protect\cite{527120:11974311} \mbox{}\protect\newline Electrohydro-dynamic Direct-Write (EDW) \unskip~\protect\cite{527120:11974328}}-{\textgreater} Direct writing of hierarchical micro/nano fibers have recently gained popularity in flexible/stretchable electronics due to its low cost, simple process and high throughput. A kinetically controlled mechanoelectrospinning (MES) is developed to directly write diversified hierarchical micro/nano fibers in a continuous and programmable manner. Unlike conventional near-field electrospinning, our MES method introduces a mechanical drawing force, to simultaneously enhance the positioning accuracy and morphology controllability. The MES is predominantly controlled by the substrate speed, the nozzle-to-substrate distance, and the applied voltage. As a demonstration, smooth straight, serpentine, self-similar, and bead-on-string structures are direct-written on silicon/elastomer substrates with a resolution of 200 nm. It is believed that MES can promote the low-cost, high precision fabrication of flexible/stretchable electronics or enable the direct writing of the sacrificial structures for nano scale lithography.

AC pulse-modulated electrohydrodynamic direct-writing (EDW) was utilized to direct-write orderly micro/nano fibrous structure on the flexible insulating polyethylene terephthalate (PET) substrate. During the EDW process, AC electrical field induced charges to reciprocate along the jet and decreased the charge repulsive force that applied on charged jet. Thanks to the smaller charge repulsive force, stable straight jet can be built up to direct-write orderly micro/nano fibrous structures on the insulating substrate. The minimum motion velocity required to direct-write straight line fibrous structure on insulating PET substrate was 700 mm/s. Moreover, the influences of AC voltage amplitude, frequency, and duty cycle ratio on the line width of fibrous structures were investigated. This work proposes a novel solution to overcome the inherent charge repulsion emerging on the insulating substrate, and promotes the application of EDW technology on the flexible electronics. [1]. {\textless}-

\subsection{Mechano-Electrospinning \unskip~\protect\cite{527120:11974304}}-{\textgreater} A mechano-electrospinning method is presented to direct-write oriented nano fiber with high deposition accuracy in continuously tunable manner. This method uses a large nozzle to deposit high-resolution fiber-arrays by near-field localization. Due to the existence of mechanical drawing force, a higher resolution pattern can be direct-written by a lower voltage, which just keeps the Taylor cone stable. Then the fiber is stretched through a moving substrate, by which the deposited fiber can be continuously tuned from 400nm to 200nm in a linear relation- ship. The effects of the speed on the diameter and morphology of fibers are studied, and the analysis of the mechanism of the fiber alignment is given. The positionability and controllability make mechano-electrospinning very different from the traditional electrospinning, which only collects the fibers in the form of nonwoven fabric. In addition, the fibers fabricated by this method can directly deposit over a large flat area in the form of arrays and complex patterns with high precision. {\textless}-

\subsection{Suspension NFES \unskip~\protect\cite{527120:12033656}}-{\textgreater} Near-field electrospinning (NFES) is widely recognized as a versatile nano fabrication method, one suitable for applications in tissue engineering. Rapid developments in this field have given rise to layered nano fibrous scaffolds. However, this electrostatic fabrication process is limited by the electric field inhibitory effects of polymer deposition. This leads to a major challenge: how to surpass this limitation on planar/layered constructs. While the current focus in this area largely lies with the investigation of new materials, techniques and increasing precision of NFES systems and patterning, exploration of complex collector substrates is often restricted by (i) available technology and (ii) access to complex electrode manufacturing tools. To achieve nano fiber arrays suspended in free space, this paper documents both the development of an integrated NFES system and the potential of standing electrodes manufactured via selective laser melting. This system was first tested by 2D patterning on planar silicon, using polyethylene oxide polymer solution. To demonstrate suspension NFES, two patterns operating within and around the standing electrodes produced high volume suspended nano arrays. Image analysis of the arrays allowed for the assessment of fiber directionality and isotropy. By scanning electron microscopy, it was found that a mean fiber diameter of 310 nm of the arrays was achieved. Effectively maneuvering between the electrode pillars required a precision automated system (unavailable off-the-shelf), developed in-house. This technique can be applied to the fabrication of nano fiber structures of sufficient volume for tissue engineering. {\textless}-

\subsection{Helix Electrohydro-dynamic Printing (HE-printing) \unskip~\protect\cite{527120:11974308} \mbox{}\protect\newline Electrohydro-dynamic (EHD) jet printing \unskip~\protect\cite{527120:11974320}}-{\textgreater} Micro/nano serpentine structures have widespread applications in flexible/stretchable electronics; however, challenges still exist for low-cost, high-efficiency and controllable manufacturing. Helix electrohydrodynamic printing (HE-printing) has been proposed here to realize controllable direct-writing of large area, highly aligned serpentine micro/nano fibers by introducing the rope coiling effect into printing process. By manipulating the flying trajectory and solidification degree of the micro/nano jet, the solidified micro/nano fiber flying in a stabilized helical manner and versatile serpentine structures deposited on a moving collector have been achieved. Systematic experiments and theoretical analysis were conducted to study the transformation behavior and the size changing rules for various deposited micro structures, and highly aligned serpentine microfibers were directly written by controlling the applied voltage, nozzle-to-collector distance and collector velocity. Furthermore, a hyper-stretchable piezoelectric device that can detect stretching, bending and pressure has been successfully fabricated using the printed serpentine micro/nano fibers, demonstrating the potential of HE-printing in stretchable electronics manufacturing.

Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine noz- zle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity. In this article, the EHD jet printing system is utilized to print patterns of polystyrene (PS) nano fibers. The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated. The EHD jet printing technology is further utilized to print various patterns of polydiacetylene (PDA)-embedded PS nano fibers. The EHD jet printing based nano fiber printing is advantageous over conventional electrospining based approaches in terms of patterned PDA images. In addition, an advanced EHD jet printing system which is adopted for aligned nano fiber printing will expand the application of nano fibers from bio and chemical sensors to tissue engineering and electronics. {\textless}-

\subsection{Airflow-assisted Electrohydro-dynamic Direct-writing (EDW) \unskip~\protect\cite{527120:11974312}}-{\textgreater} Electrohydrodynamic direct-writing (EDW) is a developing technology for high-resolution printing. How to decrease the line width and improve the deposition accuracy of direct-written patterns has been the key to the promotion for the further application of EDW. In this paper, an airflow-assisted spinneret for electrohydrodynamic direct-writing was designed. An assisted laminar airflow was introduced to the EDW process, which provided an additional stretching and constraining force on the jet to reduce the surrounding interference and enhance jet stability. The flow field and the electric field around the spinneret were simulated to direct the structure design of the airflow-assisted spinneret. Then, a series of experiments were conducted, and the results verified the spinneret design and demonstrated a stable ejection of jet in the EDW process. With assisted airflow, the uniformity of printed patterns and the deposition position accuracy of a charged jet can be improved. Complex patterns with positioning errors of less than 5\% have been printed and characterized, which provide an effective way to promote the integration of micro/nano systems. {\textless}-

>>>>

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%
\documentclass[3p,,preprint,12pt]{elsarticle}
\makeatletter\if@twocolumn\PassOptionsToPackage{switch}{lineno}\else\fi\makeatother

@@

  \renewenvironment{abstract}{\global\setbox\absbox=\vbox\bgroup
    \hsize=\textwidth\def\baselinestretch{1}%
  \noindent\unskip\textbf{}
   \par\medskip\noindent\unskip\ignorespaces}
   {\egroup}

@@

@@

@@

\begin{document}

@@

\title{SUPPLEMENTARY INFORMATION: Polymers for Near-field Electrospinning with Spatial Control
}

@@

\end{frontmatter}

### 2020-03-14 myThesis/thesis_proposal_LaTeX/Chapters/4_Objectives.tex
organising my directories ...

\section{General objective}
Study the practice and feasibility of a new synthesis process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.

\section{Particular objectives}

>>>>

\section{General objective}
Study the practice and feasibility of a new fabrication process to achieve mass scale manufacturing of carbon nano-wires in an inexpensive, continuous, simple and reproducible manner; by the integration of mechano-electrospinning technique.

\section{Specific objectives}
